---
title: "Bench calibration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bench-calibration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{css, echo = FALSE}
.help-file {
  outline-style: dashed;
  outline-color: #aaa;
}
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette showcases the main purpose of the `acceleratum` package, which
is bench calibration of (triaxial) accelerometery devices. To do so, we will
use the `bench` dataset included in the package. 

```{r setup}
library(acceleratum)
```

```{r}
# load the bench data
data(bench)
colnames(bench)
```

The `acceleration_raw` column of the bench dataset stores accelerometery data
in burst format. For an overview of the `bench` data, consult the help file:
```{r, eval = FALSE}
?bench
```

From which an extract:
```{r, echo = FALSE, class.output="help-file"}
outfile <- tempfile(fileext = ".html")
tools:::Rd2HTML("../man/bench.Rd", out = outfile)
rawHTML <- paste(readLines(outfile), collapse="\n")
rawHTML <- gsub(".*(<h3>Details.*burst\\.).*", "\\1", rawHTML)
rawHTML <- paste0('<div class="help-file">', rawHTML, '</div>')
knitr::asis_output(htmltools::htmlPreserve(rawHTML))
unlink(outfile)
```

`acceleratum` provides a helper class to process this kind of data: 
`aclrtm_burst`.
An `aclrtm_burst` object can be initialised from a data frame with `burst()`:

```{r}
bench <- burst(bench,
               data_col = "accelerations_raw",
               axes = "xyz",
               ts_col = "timestamp")

head(bench)
```

```{r, fig.height=4, fig.width=6}
plot(bench)
```

In the current version, the pipeline to estimate the scale, rotation, and bias
for calibration are implemented only for matrix-like objects. In future versions
it will become possible to work directly with data frames or 
burst objects.  
`acceleratum` provides another helper class `aclrtm_accelerometery` that is
effectively a matrix, but comes with a few methods tailored for it.
An `aclrtm_burst` object can be converted to an `aclrtm_accelerometery`
object:
```{r}
acc <- b2a(bench)
head(acc)
```

Note that an `aclrtm_accelerometery` has an (optional) attribute for
start_time, but does not retain the full timestamp sequence, which is instead
derived as needed from the `start_time` and `sampling_rate` attributes.
That is intended as the estimation of calibration parameters is
time-agnostic.

Bench calibration is carried by positioning the device at different (known)
orientations
